---
title: "CovidTracker-R Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CovidTracker-R Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=6, fig.height=4
)
```


## Introduction to CovidTrackerR

`CovidTrackerR` is a R package for basic data cleaning, wrangling and plotting 
of Covid tracking data in Canada. The package will allow you to pull data from 
the opencovid.ca API, visualize Covid related trends as a timeseries or a map, 
and calculate summary statistics of the Covid data.

## Installation
To use this package, follow the installation guide on README and 
install this package.  Then, import the package.

```{r setup}
library(CovidTrackerR)
```


## Functions

### Retrieve data using  `get_covid_data`:  
  -   This function acquires Canada Covid data of a specified type
      and for an optionally provided date and province
  -   If no arguments are given, the default is that the function
      will return cases data for all provinces and all dates.
  -   An example of when provinces and dates are provided and omitted are 
      shown below.
        
```{r 1.1.1,}
covid_data_spec <- get_covid_data('active', 'BC', '13-01-2021')
covid_data_spec
```


```{r 1.1.2}
covid_data <- get_covid_data()
head(covid_data)
```
    
### Geographical visualization with `plot_geographical`:
  -   This function creates and plots a cloropleth map of the specified 
      Covid tracking metric per province
        
```{r 1.2}
covid_df <- CovidTrackerR::get_covid_data()
plot_geographical(covid_df, cases)
```

        
### Time series visualization with `plot_timeseries`:
  -   This function creates a plot of a specified covid metric over time.
  -   Start and end dates can be optionally specified by user, if dates are
      not provided, function will create a plot over all dates in dataframe.
        
```{r 1.3}
df <- get_covid_data()
plot_timeseries(df,cases)
```

### Calculate statistical summaries with `calculate_stat_summary`:
  -   This function provides summary information about a specified 
      Covid metric in each province of Canada. It returns a dataframe
      containing statistical summaries such as the min, max, mean,
      and quartiles.
        
```{r 1.4}
covid_df <- get_covid_data()
calculate_stat_summary(covid_df,'cases')
```
